A deeper look into bug fixes: Patterns, replacements, deletions, and additions

### 2016-02-17 MSRChallenge2016.tex
update author info
Minor details

\numberofauthors{3} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Mauricio Soto\\
       \affaddr{School of Computer Science}\\
       \affaddr{Carnegie Mellon University}\\
       \affaddr{Pittsburgh, PA}\\
       \email{mauriciosoto@cmu.edu}
       % 3rd. author
\alignauthor Ferdian Thung\\
       \affaddr{University}\\
       \affaddr{City}\\
       \email{email@domain.com}
% 2nd. author
\alignauthor Chu-Pan Wong   \\
       \affaddr{Carnegie Mellon University}\\
       \affaddr{Pittsburgh, PA}\\
       \email{email@domain.com}       
\and  % use '\and' if you need 'another row' of author names
% 4th. author
\alignauthor
Claire Le Goues\\
       \affaddr{School of Computer Science}\\
       \affaddr{Carnegie Mellon University}\\
       \affaddr{Pittsburgh, PA}\\
       \email{clegoues@cs.cmu.edu}
% 5th. author
\alignauthor
David Lo\\
       \affaddr{University}\\
       \affaddr{City}\\
       \email{author@institution.edu}       
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
%\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
%email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
%(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
\date{February 2, 2016}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

@@

Automatic bug repair is the branch of computer science that deals with automated
ways to repair errors in software. There have been several approaches taken
towards improving the different methodologies to repair bugs in software
automatically~\cite{kim2013,weimer2009,legoues2012,pan2009}. A well known approach is PAR~\cite{kim2013}, which creates 10 different repair templates and applies them to the buggy code in an effort to repair
it. In this paper we have taken 7 out of the 10 PAR templates and tested how
common they are in the repairs made by programmers in the latest official data
dump of Github as of September 2015 provided by~\cite{dyer2013}.

@@

The above patterns only cover 8 \todo{inconsistent with intro} out of 10 bug fixing patterns in PAR. The other two patterns are: (1) checking that an object is an instance of a target class before casting it; and (2) replacing expression in an if condition by another expression in the same scope. Pattern (1) cannot be analyzed because Boa does not support {\em instanceof} expression. Similarly, pattern (2) requires us to track scope between pre-fix and post-fix version, which is not supported by Boa. Implementing them ourselves might be possible, but it might require too much effort than necessary. Investigating 8 out of 10 patterns should give us a good idea on how common the patterns actually are.

@@

\begin{table*}
	\centering
	\resizebox{\textwidth}{100pt}{
		\begin{tabular}{|l|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|} \hline
			&Assert&Break&Continue&Do& For&If&Label&Return&Case&Switch& Synchronized&Throw&Try&TypeDecl&While
			\\ \hline

\texttt{Assert}	&-&7.48&3.76&0.53&8.30&23.05&0.31&20.04&4.90&4.62&1.30&13.50&7.23&0.03&4.95
\\ \hline
\texttt{Break} &1.00&-&4.08&0.60&9.93&26.03&0.13&25.39&2.48&1.57&1.79&8.39&11.73&0.10&6.77
\\ \hline
\texttt{Continue} &1.74&9.42&-&1.28&11.39&18.25&0.35&22.60&3.80&2.85&2.17&8.98&9.42&0.11&7.63
\\   \hline
\texttt{Do} &0.81&5.26&6.60&0.00&9.44&14.21&0.18&15.86&3.73&1.67&1.97&5.88&6.39&0.03&27.98
\\ \hline
\texttt{For} &0.86&6.28&3.19&0.79&-&22.89&0.09&21.08&5.01&3.34&1.87&10.01&10.71&0.08&13.79
\\ \hline
\texttt{If}&1.64&8.43&2.87&0.60&13.49&-&0.24&26.46&7.45&4.80&2.85&9.89&15.11&0.08&6.11
\\ \hline
\texttt{Label} &1.30&8.33&7.86&1.11&5.18&22.85&-&15.17&3.05&2.04&14.62&10.45&4.16&0.09&3.79
\\ \hline
\texttt{Return} &1.13&9.41&3.11&0.49&13.33&27.24&0.24&-&5.59&3.65&2.55&14.91&12.61&0.12&5.61
\\ \hline
\texttt{Case} &0.78&2.84&2.84&0.39&10.27&31.79&0.16&22.40&-&0.46&2.07&7.37&11.69&0.08&6.87
\\ \hline
\texttt{Switch}&1.14&2.72&3.80&0.55&11.07&34.14&0.13&21.86&0.75&-&1.53&8.65&9.02&0.05&4.58
\\ \hline
\texttt{Synchronized} &0.80&6.57&2.28&0.43&10.21&24.18&0.05&19.77&6.35&2.07&-&9.16&12.16&0.04&5.93
\\ \hline
\texttt{Throw} &2.11&6.57&2.58&0.48&11.87&18.84&0.17&32.28&4.64&3.30&2.74&-&10.08&0.07&4.27
\\ \hline
\texttt{Try}&0.71&7.41&3.02&0.66&11.73&27.75&0.11&23.24&5.63&2.65&2.58&8.99&-&0.09&5.42
\\ \hline
\texttt{TypeDecl} &0.00&4.51&7.52&1.00&10.28&21.05&0.50&17.79&6.02&1.75&2.01&9.27&11.53&-&6.77
\\ \hline
\texttt{While}& 0.72&8.02&3.82&1.96&23.16&19.78&0.12&16.48&6.56&3.09&1.64&6.81&7.80&0.04&-
			\\ \hline
		\end{tabular}
		}
		\caption{Likelyness to replace the statement in the first column for the statement in the top row, in Java}
\end{table*}

@@

This section shows our analysis results. To begin with, we discuss the dataset
we are using, and some characteristics of real-world bug fixes. Afterwards, we
provide insights for two main categories of automatic program repair approaches.
On the one hand, many approaches \todo{citation} rely on mutation operators to
modify the source code, but we have limited knowledge about what kinds of
statements are usually modified. Our analysis results will fill in this
knowledge gap. On the other hand, some automatic program repair approaches
\todo{citation} search for specific patterns and modify source code according to
predefined templates. Our results provide evidence of how common those
patterns are in practice.

>>>>

\numberofauthors{3} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Mauricio Soto\\
       \affaddr{School of Computer Science}\\
       \affaddr{Carnegie Mellon University}\\
       \affaddr{Pittsburgh, PA}\\
       \email{mauriciosoto@cmu.edu}
       % 3rd. author
\alignauthor Ferdian Thung\\
       \affaddr{Singapore Management University}\\
       \affaddr{Singapore}\\
       \email{ferdiant.2013@smu.edu.sg}
% 2nd. author
\alignauthor Chu-Pan Wong   \\
       \affaddr{Carnegie Mellon University}\\
       \affaddr{Pittsburgh, PA}\\
       \email{email@domain.com}       
\and  % use '\and' if you need 'another row' of author names
% 4th. author
\alignauthor
Claire Le Goues\\
       \affaddr{School of Computer Science}\\
       \affaddr{Carnegie Mellon University}\\
       \affaddr{Pittsburgh, PA}\\
       \email{clegoues@cs.cmu.edu}
% 5th. author
\alignauthor
David Lo\\
\affaddr{Singapore Management University}\\
\affaddr{Singapore}\\
\email{davidlo@smu.edu.sg}       
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
%\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
%email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
%(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
\date{February 2, 2016}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

@@

Automatic bug repair is the branch of computer science that deals with automated
ways to repair errors in software. There have been several approaches taken
towards improving the different methodologies to repair bugs in software
automatically~\cite{kim2013,weimer2009,legoues2012,pan2009}. A well known approach is PAR~\cite{kim2013}, which creates 10 different repair templates and applies them to the buggy code in an effort to repair
it. In this paper we have taken 8 out of the 10 PAR templates and tested how
common they are in the repairs made by programmers in the latest official data
dump of Github as of September 2015 provided by~\cite{dyer2013}.

@@

The above patterns only cover 8 out of 10 bug fixing patterns in PAR. The other two patterns are: (1) checking that an object is an instance of a target class before casting it; and (2) replacing expression in an if condition by another expression in the same scope. Pattern (1) cannot be analyzed because Boa does not support {\em instanceof} expression. Similarly, pattern (2) requires us to track scope between pre-fix and post-fix version, which is not supported by Boa. Implementing them ourselves might be possible, but it might require too much effort than necessary. Investigating 8 out of 10 patterns should give us a good idea on how common the patterns actually are.

@@

\begin{table*}
	\centering
	\resizebox{\textwidth}{100pt}{
		\begin{tabular}{|l|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|} \hline
			&Assert&Break&Continue&Do& For&If&Label&Return&Case&Switch& Synch&Throw&Try&TypeDecl&While
			\\ \hline

\texttt{Assert}	&-&7.48&3.76&0.53&8.30&23.05&0.31&20.04&4.90&4.62&1.30&13.50&7.23&0.03&4.95
\\ \hline
\texttt{Break} &1.00&-&4.08&0.60&9.93&26.03&0.13&25.39&2.48&1.57&1.79&8.39&11.73&0.10&6.77
\\ \hline
\texttt{Continue} &1.74&9.42&-&1.28&11.39&18.25&0.35&22.60&3.80&2.85&2.17&8.98&9.42&0.11&7.63
\\   \hline
\texttt{Do} &0.81&5.26&6.60&0.00&9.44&14.21&0.18&15.86&3.73&1.67&1.97&5.88&6.39&0.03&27.98
\\ \hline
\texttt{For} &0.86&6.28&3.19&0.79&-&22.89&0.09&21.08&5.01&3.34&1.87&10.01&10.71&0.08&13.79
\\ \hline
\texttt{If}&1.64&8.43&2.87&0.60&13.49&-&0.24&26.46&7.45&4.80&2.85&9.89&15.11&0.08&6.11
\\ \hline
\texttt{Label} &1.30&8.33&7.86&1.11&5.18&22.85&-&15.17&3.05&2.04&14.62&10.45&4.16&0.09&3.79
\\ \hline
\texttt{Return} &1.13&9.41&3.11&0.49&13.33&27.24&0.24&-&5.59&3.65&2.55&14.91&12.61&0.12&5.61
\\ \hline
\texttt{Case} &0.78&2.84&2.84&0.39&10.27&31.79&0.16&22.40&-&0.46&2.07&7.37&11.69&0.08&6.87
\\ \hline
\texttt{Switch}&1.14&2.72&3.80&0.55&11.07&34.14&0.13&21.86&0.75&-&1.53&8.65&9.02&0.05&4.58
\\ \hline
\texttt{Synch} &0.80&6.57&2.28&0.43&10.21&24.18&0.05&19.77&6.35&2.07&-&9.16&12.16&0.04&5.93
\\ \hline
\texttt{Throw} &2.11&6.57&2.58&0.48&11.87&18.84&0.17&32.28&4.64&3.30&2.74&-&10.08&0.07&4.27
\\ \hline
\texttt{Try}&0.71&7.41&3.02&0.66&11.73&27.75&0.11&23.24&5.63&2.65&2.58&8.99&-&0.09&5.42
\\ \hline
\texttt{TypeDecl} &0.00&4.51&7.52&1.00&10.28&21.05&0.50&17.79&6.02&1.75&2.01&9.27&11.53&-&6.77
\\ \hline
\texttt{While}& 0.72&8.02&3.82&1.96&23.16&19.78&0.12&16.48&6.56&3.09&1.64&6.81&7.80&0.04&-
			\\ \hline
		\end{tabular}
		}
		\caption{Likelyness to replace the statement in the first column for the statement in the top row, in Java}
\end{table*}

@@

This section shows our analysis results. To begin with, we discuss the dataset
we are using, and some characteristics of real-world bug fixes. Afterwards, we
provide insights for two main categories of automatic program repair approaches.
On the one hand, some approaches rely on mutation operators to
modify the source code~\cite{legoues2012,weimer2009}, but we have limited knowledge about what kinds of
statements are usually modified. Our analysis results will fill in this
knowledge gap. On the other hand, some automatic program repair approaches~\cite{kim2013} search for specific patterns and modify source code according to
predefined templates. Our results provide evidence of how common those
patterns are in practice.
